**The Mint Scale: A Fresh Validation of the Multimodal Interoception Questionnaire and Comparison to the MAIA, BPQ and IAS**

### 2025-07-01 paper/manuscript.qmd
updated manuscript
@DominiqueMakowski I also added the PHQ-15 on the somatic section as it was not there before

We recruited 760 English-speaking participants using Prolific\textcopyright. We excluded 191 for failing at least one attention check, and 10 based on measures significantly related to the probability of failing attention checks [namely, the multivariate distance obtained with the OPTICS algorithm, @theriault2024check]. The final sample includes 559 participants (age = 37.0 $\pm$ 12.2 [18, 77]; 50.8\% women; Country of residence: 63.86% UK, 26.65% USA).
This study was approved by the University of Sussex' Ethics Committee (**NUMBER**).

@@

We recruited 921 English-speaking participants via Prolific\textcopyright and SONA, from which 118 were excluded for failing at least one attention check and 6 based on multivariate distance (using the same procedure as for study 1). 
60 participants were further excluded due to missing data following a technical error.
The final sample includes 737 participants (age = 36.8 $\pm$ 14.7 [18, 87]; 57.3\% women; Country of residence: 75.17% United Kingdom, 24.83% other).
This study was approved by the University of Sussex' Ethics Committee (**NUMBER**).

@@

##### Multidimensional Assessment of Interoceptive Awareness (MAIA)

The X items of the MAIA...

##### The Body Perception Questionnaire (BPQ)

**TODO**

##### The Interoceptive Awareness Scale (IAS)

**TODO**

@@

**TODO**

##### Emotion Reactivity Scale (ERS)

**TODO**

##### Cognitive Emotion Regulation Questionnaire (CERQ)

**TODO**

##### TODO (CEFSA)

**TODO**

@@

**TODO**

@@

**TODO**

@@

@@

**TODO**

Physical activity.

Wearables.

@@

We will start by confirming and further refining the structure of the Mint scale using the same EGA model as in Study 1. The convergent validity of the final set of items will be assessed by computing the correlations between the Mint scale and the other interoception questionnaires (MAIA, BPQ, IAS).
Then, we will test the predictive power of the Mint scale (relative to the other interoception questionnaires) on various measures.
We will start by fitting regression (linear for continuous measures - e.g., depression score - and logistic for binary

>>>>

We recruited 760 English-speaking participants using Prolific\textcopyright. We excluded 191 for failing at least one attention check, and 10 based on measures significantly related to the probability of failing attention checks [namely, the multivariate distance obtained with the OPTICS algorithm, @theriault2024check]. The final sample includes 559 participants (age = 37.0 $\pm$ 12.2 [18, 77]; 50.8\% women; Country of residence: 63.86% UK, 26.65% USA).
This study was approved by the University of Sussex' Ethics Committee (ER/MB2021/1).

@@

We recruited 921 English-speaking participants via Prolific\textcopyright and SONA, from which 118 were excluded for failing at least one attention check and 6 based on multivariate distance (using the same procedure as for study 1). 
60 participants were further excluded due to missing data following a technical error.
The final sample includes 737 participants (age = 36.8 $\pm$ 14.7 [18, 87]; 57.3\% women; Country of residence: 75.17% United Kingdom, 24.83% other).
This study was approved by the University of Sussex' Ethics Committee (ER/EB672/2).

@@

##### Multidimensional Assessment of Interoceptive Awareness - Second Version (MAIA-2)

The 37 items of the MAIA-2 [@mehling2018multidimensional] on a 7-point Likert scale from *Never* (0) to *Always* (6). The MAIA-2 consists of 8 scales: Noticing, Not-Distracting, Not-Worrying, Attention Regulation, Emotional Awareness, Self-Regulation, Body Listening and Trust. The scales address 5 dimensions of body awareness: Awareness of Body Sensations, Emotional Reaction and Attentional Response to Sensations, Capacity to Regulate Attention, Awareness of Mind-Body Integration, Trusting Body Sensations.

##### The Body Perception Questionnaire - Very Short Form (BPQ- VSF)

The 12 item BPQ-VSF [@cabrera2018assessing] related to bodily awareness on a 5-point Likert scale from *Never* (0) to *Always* (5).

##### The Interoceptive Accuracy Scale (IAS)

The 21 items of the IAS [@murphy2020testing] assessing interoceptive accuracy to physical sensations on a 5-point Likert scale ranging from *Disagree Strongly* (1) to *Strongly Agree*.

@@

The 20-items TAS [@leising2009toronto] assessing Alexithymia traits grouped into three dimensions: Difficulty Identifying Feelings, Difficulty Describing Feelings, and Externally Oriented Thinking. Items are rated in a 5-point Likert scale from *Strongly Disagree* (1) to *Strongly Agree*(5).

##### Emotion Reactivity Scale - Brief Version (B-ERS)

The 6-item B-ERS [@veilleux2024development] assessing emotional sensitivity on a 5-point Likert scale from *Not like me at all* (0) to *Extremely like me* (4).

##### Cognitive Emotion Regulation Questionnaire-short (CERQ-short)

The 18 items CERQ-short [@garnefski2006cognitive] on a 5-point Likert scale ranging from *Almost Never* (1) to *Almost Always* (5). This questionnaire measures eight cognitive responses to threatening or stressful events, including: Self-blame, Other-blame, Rumination, Catastrophizing, Putting into Perspective, Positive Refocusing, Positive Reappraisal, Acceptance, and Planning.

##### Černis Felt Sense of Anomaly scale - short-form (CEFSA-14)

The 14 item CEFSA [@vcernis2024measuring] assessing a specific sub-type of dissociative experiences in adolescence and adulthood - i.e., felt sense of anomaly-type
dissociation. the items are rated ON A 5-point Likert scale from *Never* (0) to *Always* (4), forming seven factors: Anomalous Experience of the Self, Anomalous Experience of the Body , Anomalous Experiences of Emotion , Altered Sense of Familiarity , Altered Sense of Connection, Altered Sense of Agency , and Altered Sense of Reality

@@

the 18 items PI [@clifton2021brief] measuring highest-order primal world beliefs - i.e., beliefs about the basic character of the world: Good, Safe, Enticing, Alive. Responses are scored on a 6-point Likert scale from *Strongly Disagree* (0) to *Strongly Agree* (5).

@@

The 4 item scale of the PHQ [@kroenke2009ultra] assessing depression and anxiety, with responses scored as *Not at all* (0), *Once or twice* (0.5), *Several days* (1), *More than half of the days* (2), *nearly every day* (3). This revised version added as a response option (i.e., Once or twice) as a way to improve the scale's sensitivity to milder mood fluctuations [@makowskimeasuring].

@@

##### Patient Health Questionnaire - Somatic Symptoms (PHQ-15)

The PHQ-15 [@kroenke2002phq] is comprised of 15 somatic symptoms, with responses scored as *Not at all* (0), *Bothered a little* (1) and *bothered a lot* (2).

@@

Participants were asked to report on their use of wearable devices to monitor several health indices: heart rate, number of steps, calories burned, sleep quality, and weight (including via a regular scale). For each selected index, a question appeared asking them to rate how often they check that index; responses were scored as *Never*, *Very rarely*, *A few times per week*, *Once a day*, *A few times per day*, and *A few times per hour*. Additionally, participants were asked to rate how important this information was to them on an 8-point Likert scale ranging from *Not at all* (0) to *Very much* (7).

Questions regarding physical activity were also included. Participants were asked to rate how physically active they consider themselves on an 8-point Likert scale, from *Not at all* (0) to *Very much* (7), and to self-report how many hours of active workout they engage in per week.

@@

We will start by confirming and further refining the structure of the Mint scale using the same EGA model as in Study 1. The convergent validity of the final set of items will be assessed by computing the correlations between the Mint scale and the other interoception questionnaires (MAIA, BPQ, IAS).
Then, we will test the predictive power of the Mint scale (relative to the other interoception questionnaires) on various measures.
We will start by fitting regression (linear for continuous measures - e.g., depression score - and logistic for binary...)
